---
title: "Description of the package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Description of the package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753xwFA23)
```

# Introduction

This package contains a few of the functions and datasets that were used throughout the MATH 4753 course. 

## findz()

This function takes a vector as an argument and finds the z-score of each value based on the mean and standard deviation of the data in the given vector. Using the fire dataset contained in the package, the function returns a vector containing all the z-scores.

```{r}
z <- findz(fire$DAMAGE)
z
```


## mybin()

This function simulates a binomial experiment with a given sample size and probability $0 \leq p \leq 1$ over a number of iterations, more iterations leading to a more accurate result. It returns a barplot representing the results of the experiment as well as a corresponding list of ratios for each value.

```{r}
mybin(iter = 1000, n = 20, p = 0.3)
```

## myci()

This function constructs a 95% confidence interval for the population mean given a vector of the sample data. Using the fire data set, we are 95% confident that the population mean lies in the interval.

```{r}
myci(fire$DAMAGE)
```


## myncurve()

This function calculates the lower tail probability of a normal distribution given the mean, standard deviation, and target value. It returns the result as well as a graph with the calculated area colored in orange.

```{r}
myncurve(mu = 6, sigma = 3, a = 1)
```




